Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made modifications, finished hyp one

# Theme Prevelance Hypothesis
```{r Data Preparation}
# Data preparation: Select relevant text data
comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text)) # Replace 'Content' with the actual column name containing text data

# Text preprocessing
comments_corpus <- comments_corpus %>%
  tm_map(content_transformer(tolower)) %>%  # Convert text to lowercase
  tm_map(removePunctuation) %>%              # Remove punctuation
  tm_map(removeNumbers) %>%                  # Remove numbers
  tm_map(removeWords, stopwords("english")) %>%  # Remove common stop words
#  tm_map(stemDocument) %>%                   # Perform stemming
  tm_map(stripWhitespace)                    # Strip whitespace

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 500),  # Fewer iterations for quicker results
  mc.cores = 6L,
  verbose = TRUE
)
```

@@

```{r LDA Model}
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 5, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```

@@

# Assuming top_terms_df is your data frame from the LDA analysis

@@

reshaped_df <- reshaped_df %>%
  select(term_id, 
         starts_with("Topic_1_term"), starts_with("Topic_1_beta"),
         starts_with("Topic_2_term"), starts_with("Topic_2_beta"),
         starts_with("Topic_3_term"), starts_with("Topic_3_beta"),
         starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
         starts_with("Topic_5_term"), starts_with("Topic_5_beta"))

# Create a styled table using sjPlot
# tab_df(
#  reshaped_df,
#  title = "Top Terms and Betas for Each Topic",
#  show.rownames = FALSE,
#  digits = 2,
#  file = output_file_path
#  )

@@

# Create the gt table
gt_table <- reshaped_df %>%
  gt() %>%
  tab_spanner(
    label = "Topic 1",
    columns = c("Topic_1_term", "Topic_1_beta")
  ) %>%
  tab_spanner(
    label = "Topic 2",
    columns = c("Topic_2_term", "Topic_2_beta")
  ) %>%
  tab_spanner(
    label = "Topic 3",
    columns = c("Topic_3_term", "Topic_3_beta")
  ) %>%
  tab_spanner(
    label = "Topic 4",
    columns = c("Topic_4_term", "Topic_4_beta")
  ) %>%
  tab_spanner(
    label = "Topic 5",
    columns = c("Topic_5_term", "Topic_5_beta")
  ) %>%
  cols_label(
    term_id = "Term No.",
    Topic_1_term = "term", Topic_1_beta = "beta",
    Topic_2_term = "term", Topic_2_beta = "beta",
    Topic_3_term = "term", Topic_3_beta = "beta",
    Topic_4_term = "term", Topic_4_beta = "beta",
    Topic_5_term = "term", Topic_5_beta = "beta"
  )

@@

# Create intuitive topic names based on LDA results
topic_names <- c(
  "Medical Testing & Treatment",
  "Personal Experiences & Opinions",
  "Disease Research & Transmission",
  "Sexual Orientation & Behavior",
  "Social Discussion & Impact"
)
term_topic_df$topic_name <- topic_names[term_topic_df$topic]

>>>>

# Theme Prevelance Hypothesis
```{r Data Preparation}
# Load required libraries
library(tm)

# Data preparation: Select relevant text data
comments_corpus <- Corpus(VectorSource(filtered_comments$Full.Text))  # Replace 'Full.Text' with the actual column name containing text data

# Text preprocessing
comments_corpus <- comments_corpus %>%
  tm_map(content_transformer(tolower)) %>%                   # Convert text to lowercase
  tm_map(content_transformer(function(x) gsub("[^[:alnum:] ]", " ", x))) %>%  # Remove non-alphanumeric characters
  tm_map(removePunctuation) %>%                               # Remove punctuation
  tm_map(removeNumbers) %>%                                   # Remove numbers
  tm_map(removeWords, stopwords("english")) %>%               # Remove common stop words
  # tm_map(stemDocument) %>%                                  # Perform stemming (optional)
  tm_map(stripWhitespace)                                     # Strip whitespace

@@

```{r How Many Topics, eval=FALSE, include=FALSE}
# Optimize LDA to find the best number of topics
set.seed(123)
result <- FindTopicsNumber(
  dtm,
  topics = seq(from = 2, to = 10, by = 1),  # Narrow topic range for faster computation
  metrics = c("Griffiths2004", "Deveaud2014", "CaoJuan2009", "Arun2010"),  # Use fewer metrics
  method = "Gibbs",
  control = list(seed = 123, iter = 200),  # Fewer iterations for quicker results
  mc.cores = 2L,
  verbose = TRUE
)
```

@@

```{r LDA Model}
set.seed(123) # Set seed for reproducibility
lda_model <- LDA(dtm, k = 6, control = list(seed = 123)) # 'k' is the number of topics, adjust as needed
```

@@

# Visualize the top terms for each topic (concise visualization)
top_terms_df <- tidy(lda_model, matrix = "beta") %>%
  group_by(topic) %>%
  top_n(20, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

# Round beta values to 3 decimal places
top_terms_df <- top_terms_df %>%
  mutate(beta = round(beta, 3))

@@

reshaped_df <- reshaped_df %>%
  select(term_id, 
         starts_with("Topic_1_term"), starts_with("Topic_1_beta"),
         starts_with("Topic_2_term"), starts_with("Topic_2_beta"),
         starts_with("Topic_3_term"), starts_with("Topic_3_beta"),
         starts_with("Topic_4_term"), starts_with("Topic_4_beta"),
         starts_with("Topic_5_term"), starts_with("Topic_5_beta"),
         starts_with("Topic_6_term"), starts_with("Topic_6_beta"))

@@

# Create the gt table
gt_table <- reshaped_df %>%
  gt() %>%
  tab_spanner(label = "Topic 1", columns = c("Topic_1_term", "Topic_1_beta")) %>%
  tab_spanner(label = "Topic 2", columns = c("Topic_2_term", "Topic_2_beta")) %>%
  tab_spanner(label = "Topic 3", columns = c("Topic_3_term", "Topic_3_beta")) %>%
  tab_spanner(label = "Topic 4", columns = c("Topic_4_term", "Topic_4_beta")) %>%
  tab_spanner(label = "Topic 5", columns = c("Topic_5_term", "Topic_5_beta")) %>%
  tab_spanner(label = "Topic 6", columns = c("Topic_6_term", "Topic_6_beta")) %>%
  cols_label(
    term_id = "Term No.",
    Topic_1_term = "term", Topic_1_beta = "beta", 
    Topic_2_term = "term", Topic_2_beta = "beta",
    Topic_3_term = "term", Topic_3_beta = "beta", 
    Topic_4_term = "term", Topic_4_beta = "beta",
    Topic_5_term = "term", Topic_5_beta = "beta", 
    Topic_6_term = "term", Topic_6_beta = "beta")

@@

# Create intuitive topic names based on LDA results
topic_names <- c(
  "Topic 1",
  "Topic 2",
  "Topic 3",
  "Topic 4",
  "Topic 5",
  "Topic 6"
)
term_topic_df$topic_name <- topic_names[term_topic_df$topic]
